Submissions and selectivity of *eLife* over time.

### 2019-02-25 figures/gatekeeper_representation/gatekeeper_representation.rmd
made final upadtes to code before revisions. Tweaked figure titles and sizes

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "****", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}
```

@@

p1 <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "gender") %>%
  left_join(sig_df, by = c("gender", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = gender, y = prop, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.1), size = 3) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 1.5, y = 0.9)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "right"
  ) +
  labs(y = "Proportion") +
  guides(fill = F)

@@

p2 <- people %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  filter(continent != "Antarctica") %>%
  group_by(type, continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "continent") %>%
  left_join(sig_df, by = c("continent", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    continent = reorder(continent, -prop),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = continent, y = prop, fill = continent)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.05), size = 2) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 3.5, y = 0.92)) +
  geom_segment(aes(x = 1, xend = 6, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    axis.title.x = element_blank()
  ) +
  labs(y = "Proportion") +
  scale_fill_brewer(palette = "Set2")

>>>>

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "***", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}
```

@@

p1 <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "gender") %>%
  left_join(sig_df, by = c("gender", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = gender, y = prop, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.1), size = 3) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 1.5, y = 0.9)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "right",
    plot.title = element_text(size = 18)
  ) +
  labs(y = "Proportion",
       title = "A") +
  guides(fill = F)

@@

p2 <- people %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  filter(continent != "Antarctica") %>%
  group_by(type, continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "continent") %>%
  left_join(sig_df, by = c("continent", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    continent = reorder(continent, -prop),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = continent, y = prop, fill = continent)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.05), size = 2) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 3.5, y = 0.92)) +
  geom_segment(aes(x = 1, xend = 6, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    axis.title.x = element_blank(),
    plot.title = element_text(size = 18)
  ) +
  labs(y = "Proportion",
       title = "B") +
  scale_fill_brewer(palette = "Set2")

### 2019-02-25 figures/gatekeeper_representation/reviewing_editor_continental_composition.rmd
made final upadtes to code before revisions. Tweaked figure titles and sizes

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "****", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}

>>>>

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "***", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}

### 2019-02-25 figures/selectivity_over_time/selectivity_over_time.rmd
made final upadtes to code before revisions. Tweaked figure titles and sizes

p1 <- d1 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "# Manuscripts"
  ) +
  scale_color_manual(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted"), values = c("black", "blue", "red")) +
  scale_shape_discrete(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted")) +
  scale_linetype_discrete(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted"))

@@

p2 <- d2 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  ylim(0, 1) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "%"
  ) +
  scale_color_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"), 
                     values = c("blue", "purple", "red")) +
  scale_shape_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"),
                     values = c(17, 15, 18)) +
  scale_linetype_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"), 
                          values = c("dotted", "dashed", "dotdash"))

>>>>

p1 <- d1 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "# Manuscripts",
    title = "A"
  ) +
  theme(plot.title = element_text(size = 18)) +
  scale_color_manual(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted"), values = c("black", "blue", "red")) +
  scale_shape_discrete(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted")) +
  scale_linetype_discrete(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted"))

@@

p2 <- d2 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  ylim(0, 1) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "%",
    title = "B"
  ) +
  theme(plot.title = element_text(size = 18)) +
  scale_color_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"), 
                     values = c("blue", "purple", "red")) +
  scale_shape_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"),
                     values = c(17, 15, 18)) +
  scale_linetype_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"), 
                          values = c("dotted", "dashed", "dotdash"))
